%==============================================================================
% tento soubor pouzijte jako zaklad
% this file should be used as a base for the thesis
% Autoři / Authors: 2008 Michal Bidlo, 2019 Jaroslav Dytrych
% Kontakt pro dotazy a připomínky: sablona@fit.vutbr.cz
% Contact for questions and comments: sablona@fit.vutbr.cz
%==============================================================================
% kodovani: UTF-8 (zmena prikazem iconv, recode nebo cstocs)
% encoding: UTF-8 (you can change it by command iconv, recode or cstocs)
%------------------------------------------------------------------------------
% zpracování / processing: make, make pdf, make clean
%==============================================================================
% Soubory, které je nutné upravit nebo smazat: / Files which have to be edited or deleted:
%   projekt-20-literatura-bibliography.bib - literatura / bibliography
%   projekt-01-kapitoly-chapters.tex - obsah práce / the thesis content
%   projekt-01-kapitoly-chapters-en.tex - obsah práce v angličtině / the thesis content in English
%   projekt-30-prilohy-appendices.tex - přílohy / appendices
%   projekt-30-prilohy-appendices-en.tex - přílohy v angličtině / appendices in English
%==============================================================================
\documentclass[english]{fitthesis} % bez zadání - pro začátek práce, aby nebyl problém s překladem
%\documentclass[english]{fitthesis} % without assignment - for the work start to avoid compilation problem
%\documentclass[zadani]{fitthesis} % odevzdani do wisu a/nebo tisk s barevnými odkazy - odkazy jsou barevné
%\documentclass[english,zadani]{fitthesis} % for submission to the IS FIT and/or print with color links - links are color
%\documentclass[zadani,print]{fitthesis} % pro černobílý tisk - odkazy jsou černé
%\documentclass[english,zadani,print]{fitthesis} % for the black and white print - links are black
%\documentclass[zadani,cprint]{fitthesis} % pro barevný tisk - odkazy jsou černé, znak VUT barevný
%\documentclass[english,zadani,cprint]{fitthesis} % for the print - links are black, logo is color
% * Je-li práce psaná v anglickém jazyce, je zapotřebí u třídy použít 
%   parametr english následovně:
%   If thesis is written in English, it is necessary to use 
%   parameter english as follows:
%      \documentclass[english]{fitthesis}
% * Je-li práce psaná ve slovenském jazyce, je zapotřebí u třídy použít 
%   parametr slovak následovně:
%   If the work is written in the Slovak language, it is necessary 
%   to use parameter slovak as follows:
%      \documentclass[slovak]{fitthesis}
% * Je-li práce psaná v anglickém jazyce se slovenským abstraktem apod., 
%   je zapotřebí u třídy použít parametry english a enslovak následovně:
%   If the work is written in English with the Slovak abstract, etc., 
%   it is necessary to use parameters english and enslovak as follows:
%      \documentclass[english,enslovak]{fitthesis}

% Základní balíčky jsou dole v souboru šablony fitthesis.cls
% Basic packages are at the bottom of template file fitthesis.cls
% zde můžeme vložit vlastní balíčky / you can place own packages here

% Kompilace po částech (rychlejší, ale v náhledu nemusí být vše aktuální)
% Compilation piecewise (faster, but not all parts in preview will be up-to-date)
% \usepackage{subfiles}

% Nastavení cesty k obrázkům
% Setting of a path to the pictures
%\graphicspath{{obrazky-figures/}{./obrazky-figures/}}
%\graphicspath{{obrazky-figures/}{../obrazky-figures/}}

%---rm---------------
\renewcommand{\rmdefault}{lmr}%zavede Latin Modern Roman jako rm / set Latin Modern Roman as rm
%---sf---------------
\renewcommand{\sfdefault}{qhv}%zavede TeX Gyre Heros jako sf
%---tt------------
\renewcommand{\ttdefault}{lmtt}% zavede Latin Modern tt jako tt

% vypne funkci šablony, která automaticky nahrazuje uvozovky,
% aby nebyly prováděny nevhodné náhrady v popisech API apod.
% disables function of the template which replaces quotation marks
% to avoid unnecessary replacements in the API descriptions etc.
\csdoublequotesoff



\usepackage{url}


% =======================================================================
% balíček "hyperref" vytváří klikací odkazy v pdf, pokud tedy použijeme pdflatex
% problém je, že balíček hyperref musí být uveden jako poslední, takže nemůže
% být v šabloně
% "hyperref" package create clickable links in pdf if you are using pdflatex.
% Problem is that this package have to be introduced as the last one so it 
% can not be placed in the template file.
\ifWis
\ifx\pdfoutput\undefined % nejedeme pod pdflatexem / we are not using pdflatex
\else
  \usepackage{color}
  \usepackage[unicode,colorlinks,hyperindex,plainpages=false,pdftex]{hyperref}
  \definecolor{hrcolor-ref}{RGB}{223,52,30}
  \definecolor{hrcolor-cite}{HTML}{2F8F00}
  \definecolor{hrcolor-urls}{HTML}{092EAB}
  \hypersetup{
	linkcolor=hrcolor-ref,
	citecolor=hrcolor-cite,
	filecolor=magenta,
	urlcolor=hrcolor-urls
  }
  \def\pdfBorderAttrs{/Border [0 0 0] }  % bez okrajů kolem odkazů / without margins around links
  \pdfcompresslevel=9
\fi
\else % pro tisk budou odkazy, na které se dá klikat, černé / for the print clickable links will be black
\ifx\pdfoutput\undefined % nejedeme pod pdflatexem / we are not using pdflatex
\else
  \usepackage{color}
  \usepackage[unicode,colorlinks,hyperindex,plainpages=false,pdftex,urlcolor=black,linkcolor=black,citecolor=black]{hyperref}
  \definecolor{links}{rgb}{0,0,0}
  \definecolor{anchors}{rgb}{0,0,0}
  \def\AnchorColor{anchors}
  \def\LinkColor{links}
  \def\pdfBorderAttrs{/Border [0 0 0] } % bez okrajů kolem odkazů / without margins around links
  \pdfcompresslevel=9
\fi
\fi
% Řešení problému, kdy klikací odkazy na obrázky vedou za obrázek
% This solves the problems with links which leads after the picture
\usepackage[all]{hypcap}
\usepackage{listings}

% Informace o práci/projektu / Information about the thesis
%---------------------------------------------------------------------------
\projectinfo{
  %Prace / Thesis
  project={DP},            %typ práce BP/SP/DP/DR  / thesis type (SP = term project)
  year={2022},             % rok odevzdání / year of submission
  date=\today,             % datum odevzdání / submission date
  %Nazev prace / thesis title
  title.cs={Konfigurateľná paralelná exekúcia systémových testov v rámci projektu Strimzi},  % název práce v češtině či slovenštině (dle zadání) / thesis title in czech language (according to assignment)
  title.en={Configurable parallel execution of system tests within the Strimzi project}, % název práce v angličtině / thesis title in english
  %title.length={14.5cm}, % nastavení délky bloku s titulkem pro úpravu zalomení řádku (lze definovat zde nebo níže) / setting the length of a block with a thesis title for adjusting a line break (can be defined here or below)
  %sectitle.length={14.5cm}, % nastavení délky bloku s druhým titulkem pro úpravu zalomení řádku (lze definovat zde nebo níže) / setting the length of a block with a second thesis title for adjusting a line break (can be defined here or below)
  %dectitle.length={14.5cm}, % nastavení délky bloku s titulkem nad prohlášením pro úpravu zalomení řádku (lze definovat zde nebo níže) / setting the length of a block with a thesis title above declaration for adjusting a line break (can be defined here or below)
  %Autor / Author
  author.name={Maroš},   % jméno autora / author name
  author.surname={Orsák},   % příjmení autora / author surname 
  author.title.p={Bc.}, % titul před jménem (nepovinné) / title before the name (optional)
  %author.title.a={Ph.D.}, % titul za jménem (nepovinné) / title after the name (optional)
  %Ustav / Department
  department={UITS}, % doplňte příslušnou zkratku dle ústavu na zadání: UPSY/UIFS/UITS/UPGM / fill in appropriate abbreviation of the department according to assignment: UPSY/UIFS/UITS/UPGM
  % Školitel / supervisor
  supervisor.name={Milan},   % jméno školitele / supervisor name 
  supervisor.surname={Češka},   % příjmení školitele / supervisor surname
  supervisor.title.p={Doc. RNDr.},   %titul před jménem (nepovinné) / title before the name (optional)
  supervisor.title.a={Ph.D.},    %titul za jménem (nepovinné) / title after the name (optional)
  % Klíčová slova / keywords
  keywords.cs={Strimzi, Kubernetes, Orchestrácia, Klastering, Azure, Openstack, AWS, Apache Kafka, Distribuované systémy, middleware, systémové testy, paralelizmus, multi-vláknové vykonávanie, súbeh, sychronizácia, škálovateľnosť, operátory}, % klíčová slova v českém či slovenském jazyce / keywords in czech or slovak language
  % Abstrakt / Abstract
  abstract.cs={
        V posledných rokoch mnoho spoločností prijalo Kubernetes a architektúru mikroslužieb, ktorú umožňuje.
        Táto technológia otvorila nové možností nielen pre veľké spoločnosti, ale aj pre malých vývojárov softvéru.
        Kubernetes je systém riadenia kontajnerov a nedávno sa objavil nový koncept, ako efektívnejšie organizovať kontajnery \---\ vzor operátora.
        Jeden takýto operátor je vyvinutý a udržiavaný v rámci open-source projektu s názvom Strimzi.
        Projekt Strimzi spája niekoľko nástrojov, ktoré sa starajú o nasadenie Apache Kafka na Kubernetes.
        Keďže Kafka je komplexný, horizontálne škálovateľný, distribuovaný systém, viete si predstaviť, že jeho inštalácia je pomerne zložitá akcia.
        Preto jednou z najväčších výziev používania Kubernetes je, ako efektívne a rýchlo otestovať projekty ako Kafka a Strimzi a zároveň overiť integráciu s inými podobnými produktmi.
        Zdroje, ktoré potrebuje Kubernetes, sú oveľa náročnejšie v porovnaní s nasadením Kafka na virtuálne stroje alebo typické inštancie kontajnerov.
        Aby sme tento problém vyriešili, prijali sme princípy paralelného vykonávania a vytvorili mechanizmus v rámci systémových testov Strimzi, ktorý paralelne spúšťa testy iba proti jedinému klastru Kubernetes.
        Okrem toho sme navrhli úplne novú architektúru pre end-to-end testy.
        Vylepšenia sú zamerané na \textit{škálovateľnosť} a \textit{skrátenie času vykonávania}.
        Prostredníctvom niekoľkých experimentov táto práca ukazuje, že navrhovaný mechanizmus s rôznymi konfiguráciami klastra Kubernetes (vrátane \textit{počet uzlov Kubernetes}, \textit{počet paralelne vykonávaných testov a sád}) výrazne urýchlil vykonávanie testov.}, % abstrakt v českém či slovenském jazyce / abstract in czech or slovak language
  abstract.en={
        In recent years, many companies have adopted Kubernetes and the microservices architecture it enables.
        This technology was opened up many new possibilities not just for large companies, but also for small software developers.
        Kubernetes is a container-orchestration system and recently a new concept has emerged arround how to orchestrate the containers more efficiently \---\ the Operator pattern.
        One such operator is developed and maintained under an open-source project called Strimzi.
        The Strimzi project gathers together several tools, which take care of the deployment of Apache Kafka on Kubernetes.
        Since Kafka is a complex, horizontally scalable, distributed system, you can imagine that its installation is a relatively complex action.
        Therefore, one of the biggest challenges of using Kubernetes is how to effectively and quickly test projects such as Kafka and Strimzi and at the same time verify integration with other similar products.
        The resources needed by Kubernetes are much more demanding compared to the deployment of Kafka on virtual machines or typical container instances.
        To tackle this problem, we adopt the principles of parallel execution and created a mechanism within Strimzi system tests, which runs tests in parallel against only a single Kubernetes cluster.
        Furthermore, we proposed a brand new architecture for the end-to-end tests.
        The improvements aim at \textit{scalability} and \textit{reduction of execution time}.
        Through several experiments, this paper shows that proposed mechanism with different configurations of the Kubernetes cluster (including \textit{number of Kubernetes nodes}, \textit{number of tests and suites executed in parallel}) significantly accelerated execution of the tests.
  
  %In recent years, more and more companies adopted the %Kubernetes system and architecture of microservices. This %technology opened up new possibilities and with it came the  %operator pattern. One of the operators is also called Strimzi.
  %
  %This approach introduced a completely new pattern usable in %cloud world - Operators. One of this operators is also %Strimzi. This project collects together several tools, which %takes care about Apache Kafka deployed on top of Kubernetes. %Since Kafka is very huge, robust and easilly scalable system, %you can imagine that deployment of systems like this is not %trivial. One of the biggest challenges in this area is %effective testing of systems like Strimzi, because you combine %there together multiple huge applications. Moreover, the %resources which you need to setup Kubernetes cluster are much %more bigger than for deploy for instance Kafka on some virtual %machine. With this knowledge we can ask - how we can %effectively test operators such as Strimzi and how to avoid %false positive scenarios when several tests are running in %parallel? Those and more questions will be ansvered in this %thesis, where we will focus on current implementaton of %Strimzi system testing and how to improve it to effectively %test it in parallel with multiple operators and Kafka clusters %deployed into one Kubernetes cluster.
  
  % My version
  % Strimzi is a collection of Kubernetes operators for Apache Kafka based on the idea % to be as easily configurable as possible. Since Kafka is a distributed, % horizontally scalable middleware product, the testing itself could take much time. % Setting up Kafka cluster with other resources is time-consuming, not even speaking % about deploying Strimzi operators next to it. The current approach of testing the % Strimzi product is sluggish and running regression profile takes more than thirty % hours by using sequence execution. To tackle this problem, we adopt the principles % of parallel execution and create a mechanism, which runs end-to-end tests in % parallel against only a single Kubernetes cluster. Moreover, we proposed a brand % new architecture of the end-to-end tests. The improvements aim at % \textit{scalability} and \textit{reduction of execution time}. Through several % experiments, this paper shows that proposed mechanism with different configurations % of Kubernetes cluster (including \textit{number of Kubernetes nodes}, % \textit{number of tests or suites executed in parallel}) significantly accelerated % execution of the tests. 
  }, % klíčová slova v českém či slovenském jazyce / keywords in czech or slovak language
  keywords.en={Strimzi, Kubernetes, Orchestration, Clustering, Azure, Openstack, AWS, Apache Kafka, Distributed systems, middleware, end-to-end tests, paralelism, multi-threaded execution, race condition, synchronization, scalability, operators}, % abstrakt v anglickém jazyce / abstract in english
  %abstract.en={An abstract of the work in English will be written in this paragraph.},
  % Prohlášení (u anglicky psané práce anglicky, u slovensky psané práce slovensky) / Declaration (for thesis in english should be in english)
  declaration={
        Hereby I declare that this master’s thesis was prepared as an original author’s work under the supervision of Doc. Milan Česka,
        further information was provided by Ing. Jakub Stejskal. All the relevant information sources used during this thesis’s preparation are appropriately cited and included in the reference list.},
  %declaration={I hereby declare that this Bachelor's thesis was prepared as an original work by the author under the supervision of Mr. X
% The supplementary information was provided by Mr. Y
% I have listed all the literary sources, publications and other sources, which were used during the preparation of this thesis.},
  % Poděkování (nepovinné, nejlépe v jazyce práce) / Acknowledgement (optional, ideally in the language of the thesis)
  acknowledgment={
        I would like to thank my supervisors, Ing. Jakub Stejskal, Doc. Milan Češka and Dr. Thomas Cooper for
        their time. This thesis is realized in cooperation with Red Hat Czech, s.r.o.},
  %acknowledgment={Here it is possible to express thanks to the supervisor and to the people which provided professional help
%(external submitter, consultant, etc.).},
  % Rozšířený abstrakt (cca 3 normostrany) - lze definovat zde nebo níže / Extended abstract (approximately 3 standard pages) - can be defined here or below
  extendedabstract={
        V dnešnej dobe sa čoraz častejšie stretávame s paralelnými programami.
        Tucet programov, ktoré boli napísané typickým spôsobom pre jednojadrové systémy, nedokáže využiť prítomnosť počítačov s viacerými jadrami.
        Keď sme chceli urýchliť riešenie problémov, chceli sme vytvoriť niečo, čo by eliminovalo náš čas na výpočty.
        Tak sme vynašli počítač, ktorý na začiatku nevedel relatívne nič robiť.
        To všetko sa však po pár rokoch zmenilo a počítač vyriešil problémy, ktoré človeku zabrali veľa dní.
        V súčasnosti žijeme v dobe, kedy počítače výrazne skrátili čas vykonávania riešením rôznych problémov pomocou paralelizmu.

        Pred niekoľkými rokmi \emph{Google} vydal technológiu, ktorá definovala a zmenila našu perspektívu nasadzovania a správy aplikácií.
        Túto revolúciu spôsobil iteratívny sled malých krokov (t.j., fyzická, virtuálna a kontajnerová éra).
        \emph{Kubernetes}~\cite{kubernetes, kubernetesBook} je systém na správu kontajnerov a v ďalšej mini iterácii priniesol nový koncept, ako efektívnejšie organizovať kontajnery \---\ \emph{vzor operátora }.
        \emph{Vzor operátora} má za cieľ zachytiť, ako rozšíriť a implementovať úlohy automatizácie nad rámec \emph{Kubernetes}.
        Jeden takýto operátor je vyvinutý a udržiavaný ako súčasť projektu s otvoreným zdrojom s názvom Strimzi~\cite{strimziDoc, strimziBlogPosts}.
        Projekt \emph{Strimzi} spája niekoľko nástrojov, ktoré sa starajú o nasadenie Apache Kafka~\cite{apacheKafkaDefinitiveGuide, apacheKafkaDesignDistributedSystems, kafkaStreamsBook, kafkaDocumentation} na Kubernetes.
        Komplexnosť, horizontálna škálovateľnosť a distribučný systém;
        sú všetky atribúty \emph{Apache Kafka}.
        Žiaľ, tieto atribúty robia systém mimoriadne zložitou entitou na overenie.
        Preto je jednou z najväčších výziev používania \emph{Kubernetes} efektívne a rýchle testovanie projektov ako \emph{Kafka} a \emph{Strimzi} pri overovaní integrácie s podobnými produktmi.
        Čo sa týka zdrojov potrebných na nasadenie \emph{Kafka} na virtuálne stroje alebo kontajnery, je relatívne jednoduché porovnať nasadenie Kafku na \emph{Kubernetes}.
        Napriek tomu to spôsobuje časové problémy pri testovaní nášho projektu \emph{Strimzi}.
        Na vyriešenie tohto problému sme prijali princípy paralelného vykonávania a vytvorili mechanizmus v rámci \emph{Strimzi testov systému}, ktorý spúšťa testy paralelne iba proti jednému klastru \emph{Kubernetes}.

        Súvisiaca práca sa zameriava na zlepšenie celkového času overenia produktu Strimzi.
        Niekoľko vydaní Strimzi nám dáva empirické poznatky, že testovanie pomocou sekvenčného výpočtového modelu bolo extrémne pomalé.
        Okrem toho produkt obsahuje asi pätnásť najkritickejších možných kombinácií nasadenia produktu, z ktorých každá trvá viac ako šesťdesiat hodín.
        Tento sekvenčný výpočtový model nie je odporúčaným kandidátom na overenie takého množstva nasadení.

        Napriek tomu, ako súčasť tohto úsilia o coarse-grained paralelizmus pri vykonávaní viacerých nasadení produktov, čiastočne urýchlil celkový výpočet.
        Tento prístup však nie je horizontálne škálovateľný kvôli našim cloudovým službám, ktoré poskytujú zdroje (t.j., bare metal, virtuálne stroje, kontajnery).
        Dostali sme sa preto k poslednej príležitosti na zlepšenie výpočtov pomocou vertikálnej škálovateľnosti zdrojov (t.j., pamäte, centrálnych procesorových jednotiek), ktoré nám cloudové služby ponúkajú.
        Tieto informácie nás motivovali navrhnúť a implementovať mechanizmus fine-grained paralelizmu v našom testovacom rámci.

        Experimenty, ktoré sme vykonali nad danou implementáciou ukázali celkové zlepšenie výpočtového času na viacerých
        podmnožínách testovacích prípadov.
        Napríklad u method-wide paralelizácií sme mohli vidieť zrýchlenie z troch hodín na takmer dvadstať minút pri využití 12 vlákien
        (jednalo sa však o podmnožinu testov, ktoré všetky podporovali parallelizmus).
        Zároveň sme tak mohli vidieť zrýchlenie pri využítí reálnej produkčnej vzorky, ktorá obsahovala viac než tristo testov.
    },
  extabstract.odd={true}, % Začít rozšířený abstrakt na liché stránce? / Should extended abstract start on the odd page?
  %faculty={FIT}, % FIT/FEKT/FSI/FA/FCH/FP/FAST/FAVU/USI/DEF
  faculty.cs={Fakulta informačních technologií}, % Fakulta v češtině - pro využití této položky výše zvolte fakultu DEF / Faculty in Czech - for use of this entry select DEF above
  faculty.en={Faculty of Information Technology}, % Fakulta v angličtině - pro využití této položky výše zvolte fakultu DEF / Faculty in English - for use of this entry select DEF above
  department.cs={Ústav matematiky}, % Ústav v češtině - pro využití této položky výše zvolte ústav DEF nebo jej zakomentujte / Department in Czech - for use of this entry select DEF above or comment it out
  department.en={Institute of Mathematics} % Ústav v angličtině - pro využití této položky výše zvolte ústav DEF nebo jej zakomentujte / Department in English - for use of this entry select DEF above or comment it out
}

% Rozšířený abstrakt (cca 3 normostrany) - lze definovat zde nebo výše / Extended abstract (approximately 3 standard pages) - can be defined here or above
%\extendedabstract{Do tohoto odstavce bude zapsán výtah (abstrakt) práce v českém (slovenském) jazyce.}
% Začít rozšířený abstrakt na liché stránce? / Should extended abstract start on the odd page?
%\extabstractodd{true}

% nastavení délky bloku s titulkem pro úpravu zalomení řádku - lze definovat zde nebo výše / setting the length of a block with a thesis title for adjusting a line break - can be defined here or above
%\titlelength{14.5cm}
% nastavení délky bloku s druhým titulkem pro úpravu zalomení řádku - lze definovat zde nebo výše / setting the length of a block with a second thesis title for adjusting a line break - can be defined here or above
%\sectitlelength{14.5cm}
% nastavení délky bloku s titulkem nad prohlášením pro úpravu zalomení řádku - lze definovat zde nebo výše / setting the length of a block with a thesis title above declaration for adjusting a line break - can be defined here or above
%\dectitlelength{14.5cm}

% řeší první/poslední řádek odstavce na předchozí/následující stránce
% solves first/last row of the paragraph on the previous/next page
\clubpenalty=10000
\widowpenalty=10000

% checklist
\newlist{checklist}{itemize}{1}
\setlist[checklist]{label=$\square$}

% Nechcete-li, aby se u oboustranného tisku roztahovaly mezery pro zaplnění stránky, odkomentujte následující řádek / If you do not want enlarged spacing for filling of the pages in case of duplex printing, uncomment the following line
% \raggedbottom

\begin{document}
  % Vysazeni titulnich stran / Typesetting of the title pages
  % ----------------------------------------------
  \maketitle
  % Obsah
  % ----------------------------------------------
  \setlength{\parskip}{0pt}

  {\hypersetup{hidelinks}\tableofcontents}
  
  % Seznam obrazku a tabulek (pokud prace obsahuje velke mnozstvi obrazku, tak se to hodi)
  % List of figures and list of tables (if the thesis contains a lot of pictures, it is good)
  \ifczech
    \renewcommand\listfigurename{Seznam obrázků}
  \fi
  \ifslovak
    \renewcommand\listfigurename{Zoznam obrázkov}
  \fi
  % {\hypersetup{hidelinks}\listoffigures}
  
  \ifczech
    \renewcommand\listtablename{Seznam tabulek}
  \fi
  \ifslovak
    \renewcommand\listtablename{Zoznam tabuliek}
  \fi
  % {\hypersetup{hidelinks}\listoftables}

  \ifODSAZ
    \setlength{\parskip}{0.5\bigskipamount}
  \else
    \setlength{\parskip}{0pt}
  \fi

  % vynechani stranky v oboustrannem rezimu
  % Skip the page in the two-sided mode
  \iftwoside
    \cleardoublepage
  \fi

  % Text prace / Thesis text
  % ----------------------------------------------
  \ifenglish
    \input{chapters/01-introduction}
    \input{chapters/02-preliminaries}
    \input{chapters/02a-kubernetes}
    \input{chapters/02b-kafka}
    \input{chapters/02c-strimzi}
    \input{chapters/02d-strimzi-system-tests}
    \input{chapters/03-theory-of-paralellization}
    \input{chapters/04-proposal-of-parallel-approach}
    \input{chapters/05-implementation}
    \input{chapters/06-experiments.tex}
  \else
    \input{chapters/projekt-01-kapitoly-chapters}
  \fi
  
  % Kompilace po částech (viz výše, nutno odkomentovat)
  % Compilation piecewise (see above, it is necessary to uncomment it)
  %\subfile{projekt-01-uvod-introduction}
  % ...
  %\subfile{chapters/projekt-05-conclusion}


  % Pouzita literatura / Bibliography
  % ----------------------------------------------
  \ifslovak
  \makeatletter
  \def\@openbib@code{\addcontentsline{toc}{chapter}{Literatúra}}
  \makeatother
  \bibliographystyle{bib-styles/Pysny/skplain}
  \else
  \ifczech
  \makeatletter
  \def\@openbib@code{\addcontentsline{toc}{chapter}{Literatura}}
  \makeatother
  \bibliographystyle{bib-styles/Pysny/czplain}
  \else
  \makeatletter
  \def\@openbib@code{\addcontentsline{toc}{chapter}{Bibliography}}
  \makeatother
  \bibliographystyle{bib-styles/Pysny/enplain}
  %  \bibliographystyle{alpha}
  \fi
  \fi
  \begin{flushleft}
      \bibliography{projekt-20-literatura-bibliography}
  \end{flushleft}

  % vynechani stranky v oboustrannem rezimu
  % Skip the page in the two-sided mode
  \iftwoside
  \cleardoublepage
  \fi

  % Prilohy / Appendices
  % ---------------------------------------------
  \appendix
  \ifczech
  \renewcommand{\appendixpagename}{Přílohy}
  \renewcommand{\appendixtocname}{Přílohy}
  \renewcommand{\appendixname}{Příloha}
  \fi
  \ifslovak
  \renewcommand{\appendixpagename}{Prílohy}
  \renewcommand{\appendixtocname}{Prílohy}
  \renewcommand{\appendixname}{Príloha}
  \fi
%  \appendixpage

% vynechani stranky v oboustrannem rezimu
% Skip the page in the two-sided mode
%\iftwoside
%  \cleardoublepage
%\fi

  \ifslovak
%  \section*{Zoznam príloh}
%  \addcontentsline{toc}{section}{Zoznam príloh}
  \else
  \ifczech
%    \section*{Seznam příloh}
%    \addcontentsline{toc}{section}{Seznam příloh}
  \else
%    \section*{List of Appendices}
%    \addcontentsline{toc}{section}{List of Appendices}
  \fi
  \fi
  \startcontents[chapters]
  \setlength{\parskip}{0pt}
  % seznam příloh / list of appendices
  % \printcontents[chapters]{l}{0}{\setcounter{tocdepth}{2}}

  \ifODSAZ
  \setlength{\parskip}{0.5\bigskipamount}
  \else
  \setlength{\parskip}{0pt}
  \fi

  % vynechani stranky v oboustrannem rezimu
  \iftwoside
  \cleardoublepage
  \fi

  % Přílohy / Appendices
  \ifenglish
  \input{projekt-30-prilohy-appendices-en}
  \else
  \input{projekt-30-prilohy-appendices}
  \fi

    % Kompilace po částech (viz výše, nutno odkomentovat)
    % Compilation piecewise (see above, it is necessary to uncomment it)
    %\subfile{projekt-30-prilohy-appendices}
  
\end{document}
